Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-07 reanalysis-9-alternative_specifications.qmd
packages

@@

```{r forest-plot}
#| fig.height: 10
#| fig.width: 8

# Create forest plot matching the style of results-summary.Rmd
# Add colors for specific methods
forest_data$color <- "black"
if ("twang_gbm" %in% forest_data$method) {
  forest_data$color[forest_data$method == "twang_gbm"] <- "blue"
}

@@

log_message("Forest plot saved")
```

@@

```{r summary-table}
# Display the summary table
kable(summary_table, 
      caption = "Pooled Effect Estimates Across Propensity Score Methods",
      col.names = c("Method", "Odds Ratio", "95% CI", "P-value", "N Imputations"),
      align = c("l", "r", "c", "r", "r"))

@@

log_message("Summary table saved to CSV")
```

>>>>

# Check if we have results
if (length(pooled_results) == 0) {
  cat("\n\n*** WARNING: No pooled results available ***\n")
  cat("This could mean:\n")
  cat("1. PS methods haven't been run yet (check reanalysis-4-propensity_scores.qmd)\n")
  cat("2. Cache directory path is incorrect\n")
  cat("3. Cache files have been deleted\n\n")
  cat("Current cache directory:", cache_dir, "\n")
  cat("Looking for files like: nearest_glm_imp_1.rds\n\n")

  # Check if the alternative methods were run in step 4
  ps_cache_step4 <- file.path(reanalysis_data_dir, "ps_cache")
  if (dir.exists(ps_cache_step4)) {
    twang_files <- list.files(ps_cache_step4, pattern = "twang_imp.*\\.rds")
    if (length(twang_files) > 0) {
      cat("Found twang files in step 4 cache:", ps_cache_step4, "\n")
      cat("  Files:", paste(twang_files[1:min(3, length(twang_files))], collapse = ", "), "...\n")
    }
  }

  stop("No results to process. Please run PS methods first or check cache paths.")
}

@@

```{r forest-plot}
#| fig.height: 10
#| fig.width: 8
#| eval: !expr length(pooled_results) > 0

if (is.null(forest_data) || nrow(forest_data) == 0) {
  cat("No data available for forest plot\n")
} else {
  # Create forest plot matching the style of results-summary.Rmd
  # Add colors for specific methods
  forest_data$color <- "black"
  if ("twang_gbm" %in% forest_data$method) {
    forest_data$color[forest_data$method == "twang_gbm"] <- "blue"
  }

@@

  log_message("Forest plot saved")
}  # Close the else statement
```

@@

```{r summary-table}
#| eval: !expr length(pooled_results) > 0

if (is.null(summary_table) || nrow(summary_table) == 0) {
  cat("No summary table available\n")
} else {
  # Display the summary table
  kable(summary_table, 
        caption = "Pooled Effect Estimates Across Propensity Score Methods",
        col.names = c("Method", "Odds Ratio", "95% CI", "P-value", "N Imputations"),
        align = c("l", "r", "c", "r", "r"))

@@

  log_message("Summary table saved to CSV")
}
```
